The hydra and the rooster

### 2020-07-11 latex/chapter-hydras.tex
renaming zero_succ_limit-dec

\subsection{Termination of all battles}

% \subsection{Reachability}

% Let $b$ be an instance of \texttt{battle}.  We say that a configuration $(i,h)$ is 
% \emph{reachable} if there exists some initial hydra $h_0$ such that the transformation from $(0,h_0)$ into $(i,h)$ belongs to $b$. The following inductive definition considers also the case where $i=0$ and $h=h_0$.

% \vspace{4pt}
% \emph{From Module~\href{../src/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}

% \begin{Coqsrc}
% Inductive reachable (b : Battle)
%   : nat -> Hydra ->  Prop  :=
% | reachable_0 : forall h1, reachable b 0 h1
% | reachable_S : forall i h h0,  fight b  0 h0 i h ->
%                                 reachable b i h.
% \end{Coqsrc}

% A nice property of the classes \texttt{free} and \texttt{standard} is that every configuration $(i,h)$ is reachable. It is sufficient to add $i$ heads to $h$'s foot and start the battle at time $0$.

% \begin{Coqsrc}
% Lemma reachable_free : forall i  h, reachable free i h.

% Lemma reachable_standard  : forall h i, reachable standard i h.
% \end{Coqsrc}

We say that a kind  $B$ of battles is \emph{alive} if for any configuration $(i,h)$, where $h$ is not a head, there exists a further step in class $B$.

@@

\subsection{Some failed attempts}
The class \texttt{Hvariant} is parameterized by a well-founded order $<$ on some type $A$, a class of battles $B$ and a measure $m$. When $<$ or $m$ are 
badly given for a given class $B$, one may fail to find a variant.

@@

Let us present the main steps of that proof, the script of which  is in the module ~\href{../src/html/hydras.Hydra.Omega_Small.html}{Hydra/Omega\_Small.v} \footnote{ The name of this file means ``the ordinal $\omega$ is too small for proving the termination of [free] hydra battles ''. In effect, the elements of $\omega$, considered as a set, are just the natural numbers.}.

>>>>

@@

\subsection{Some failed attempts to prove termination}
The class \texttt{Hvariant} is parameterized by a well-founded order $<$ on some type $A$, a class of battles $B$ and a measure $m$. When $<$ or $m$ are 
badly given for a given class $B$, one may fail to find a variant.

@@

Let us present the main steps of that proof, the script of which  is in the module ~\href{../src/html/hydras.Hydra.Omega_Small.html}{Hydra/Omega\_Small.v} \footnote{ The name of this file means ``the ordinal $\omega$ is too small for proving the termination of [free] hydra battles ''. In effect, the elements of $\omega$, considered as a set, are just the natural numbers (see next chapter for more details)}.
